---
title: "German Election Polls"
author: "Valeria Morales, Lazar Jelic, Hanlu Lin, Hao Ni, Purva Sikri, Junna Yanai"
date: "9/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries, warnings=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest)
```

# Replicate German Election Plot

The Guardian newspaper has an [election poll tracker for the upcoming
German
election](https://www.theguardian.com/world/2021/aug/20/german-election-poll-tracker-who-will-be-the-next-chancellor).
The list of the opinion polls since Jan 2021 can be found at
[Wikipedia](https://en.wikipedia.org/wiki/Opinion_polling_for_the_2021_German_federal_election)
and the task is to reproduce the graph similar to the one produced by
the Guardian.

The following code will scrape the wikipedia page and import the table
in a dataframe.

```{r, scrape_wikipedia_polling_data, warnings= FALSE, message=FALSE}
url <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2021_German_federal_election"
# https://www.economist.com/graphic-detail/who-will-succeed-angela-merkel
# https://www.theguardian.com/world/2021/jun/21/german-election-poll-tracker-who-will-be-the-next-chancellor

# get tables that exist on wikipedia page
tables <- url %>% 
  read_html() %>% 
  html_nodes(css="table")

# parse HTML tables into a dataframe called polls 
# Use purr::map() to create a list of all tables in URL
polls <- map(tables, . %>% 
             html_table(fill=TRUE)%>% 
             janitor::clean_names())

# list of opinion polls
german_election_polls <- polls[[2]] %>% # the first table on the page contains the list of all opinions polls
  slice(2:(n()-1)) %>%  # drop the first row, as it contains again the variable names and last row that contains 2017 results
  mutate(
         # polls are shown to run from-to, e.g. 9-13 Aug 2021. We keep the last date, 13 Aug here, as the poll date
         # and we extract it by picking the last 11 characters from that field
         end_date = str_sub(fieldwork_date, -11),
         # end_date is still a string, so we convert it into a date object using lubridate::dmy()
         end_date = dmy(end_date),
         # we also get the month and week number from the date, if we want to do analysis by month- week, etc.
         month = month(end_date),
         week = isoweek(end_date))
```

Below is the code that recreates the plot

```{r plot replicate, warnings=FALSE}
#Select only necessary columns of the dataset
german_election_polls_cleaned <- german_election_polls %>%
  select(end_date, union, spd, af_d, fdp, linke, grune)

#Assigning colors to each political party, extracted from original plot using adobe color 
col_union <- 'black'
col_spd <- '#BF0404'
col_af_d <- '#8C1F7A'
col_fdp <- '#F2AE2E'
col_linke <- '#0A5789'
col_grune <- '#45BF41'

#Plotting the election outcomes
german_elections_plot <- german_election_polls_cleaned %>%
  ggplot +
  geom_point(aes(x=end_date, y=union, colour='black')) + #Union Party points assigned the color black
  geom_smooth(aes(x=end_date, y=union), colour='black', span=0.09, se=F) + #Union Party curve with span = 0.09 assigned the color black
  geom_point(aes(x=end_date, y=spd), colour=col_spd, alpha=0.5) + #SPD Party points assigned the color red
  geom_smooth(aes(x=end_date, y=spd), colour=col_spd, span=0.09, se=F) + #SPD Party curve with span = 0.09 assigned the color red
  geom_point(aes(x=end_date, y=af_d), colour=col_af_d, alpha=0.5) + #AfD Party points assigned the color purple
  geom_smooth(aes(x=end_date, y=af_d), colour=col_af_d, span=0.09, se=F) +  #AfD Party curve with span = 0.09 assigned the color purple
  geom_point(aes(x=end_date, y=fdp), colour=col_fdp, alpha=0.5) + #FDP Party points assigned the color yellow
  geom_smooth(aes(x=end_date, y=fdp), colour=col_fdp, span=0.09, se=F) + #FDP Party curve with span = 0.09 assigned the color yellow
  geom_point(aes(x=end_date, y=linke), colour=col_linke, alpha=0.5) + #Linke Party points assigned the color blue
  geom_smooth(aes(x=end_date, y=linke), colour=col_linke, span=0.09, se=F) + #Linke Party curve with span = 0.09 assigned the color blue
  geom_point(aes(x=end_date, y=grune), colour=col_grune, alpha=0.5) + #Grune Party points assigned the color green
  geom_smooth(aes(x=end_date, y=grune), colour=col_grune, span=0.09, se=F) + #Grune Party curve with span = 0.09 assigned the color green
  scale_y_continuous(breaks=seq(0, 40, 10), labels=c('0%', '10%', '20%', '30%', '40%')) + #Adjusting the scale
  geom_hline(yintercept=5, linetype='dashed', color='gray') + 
  scale_color_manual(name='',
                     labels = c('Union', 'SPD', 'AfD', 'FDP', 'Linke', 'Grüne'),
                     values = c('col_union'=col_union,'col_spd'=col_spd,'col_af_d'=col_af_d,'col_fdp'=col_fdp,'col_linke'=col_linke,'col_grune'=col_grune)) + #Creating a legend 
    labs(x='', y='') +
  theme_minimal() + #change theme to be more similar to the original
  theme(legend.background = element_rect(fill=NA, size=.3, linetype="solid")) + #add box around legend to be more similar to the original
  NULL

ggsave(file='germanElections_plot_home.jpg', plot=german_elections_plot, path = '~/Desktop/LBS/Term1/my-website/my-website/static/img', width=18, height=18)

ggsave(file='germanElections_plot.jpg', plot=german_elections_plot, path = '~/Desktop/LBS/Term1/my-website/my-website/static/img', width=18, height=8)
```